HO unification from object language to meta language

### 2024-04-03 paper/main.tex
wip: small update

% This property can be relaxed, to accept approximations: a dedicated
% section is given in a future section
\begin{corollary}
  If the \lhs of a \linkbeta is instantiated to a rigid term and its \rhs
  counterpart is still in \maybebeta,
  the original unification problem is not in \llambda
  % \noteE[inline]{non capisco cosa vuoi dire con "the current...". Data la prova sotto vuoi dire che il problem originale sarebbe stato fuori... e quindi falliamo}
  %\noteE[inline]{Is it clearer?}
  and the unification fails.
  \noteE[inline]{it is clear. Quello che manca è percè serve farlo, e che cosa si guadagna. Qui dimostri che fallire "ha senso" se siamo solo interessati a llambda, ma allo stesso tempo sti beta link sono lì per gestire roba fuori.}
\end{corollary}

@@

>>>>

% This property can be relaxed, to accept approximations: a dedicated
% section is given in a future section
\begin{corollary}
  If the \lhs of a \linkbeta is instantiated to a rigid term and its \rhs
  counterpart is still in \maybebeta,
  the original unification problem is not in \llambda
  % \noteE[inline]{non capisco cosa vuoi dire con "the current...". Data la prova sotto vuoi dire che il problem originale sarebbe stato fuori... e quindi falliamo}
  %\noteE[inline]{Is it clearer?}
  and the unification fails.
  \label{cor:keep-fidelity}
\end{corollary}

@@

\begin{lemma}
  Given a \hoUnifPb and a substitution $\sigma$ then the resolution of
  $\sigma\hoUnifPb$ guarantees \cref{prop:fidelity} 
\end{lemma}

\begin{proof}[Proof sketch]
  If $\sigma\hoUnifPb$ is in \llambda, then by \cref{DA FARE}, the problem 
  unifies iff its corresponding \Fo{} unifies too. If $\sigma\hoUnifPb$ is in 
  \maybebeta, then, by \cref{cor:keep-fidelity}, the unification fails, as per
  the corresponding unification in \Fo{}.
\end{proof}

\noteD[inline]{manca una ref che dice che se \hoUnifPb is not in $\llambda$ but
$\sigma\hoUnifPb$ is in \llambda, then \hoUnifPb succeeds iff its corresponding
\Fo{} pb succeeds}.
